### 2014-09-25 LaTeX/mCitySimPlot.tex
updates to tex, and plots

% Created by tikzDevice version 0.7.0 on 2014-09-23 11:39:59
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (433.62,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 39.69, 34.03) rectangle (421.57,277.03);
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[fill=fillColor] ( 39.69, 34.03) rectangle (421.57,277.03);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 57.05,110.46) --
	( 62.08,112.14) --
	( 67.11,113.83) --
	( 72.14,115.51) --
	( 77.17,117.20) --
	( 82.20,118.88) --
	( 87.23,120.57) --
	( 92.27,122.25) --
	( 97.30,123.94) --
	(102.33,125.62) --
	(107.36,127.30) --
	(112.39,128.99) --
	(117.42,130.67) --
	(122.45,132.36) --
	(127.49,134.04) --
	(132.52,135.73) --
	(137.55,137.41) --
	(142.58,139.10) --
	(147.61,140.78) --
	(152.64,142.47) --
	(157.67,144.15) --
	(162.71,145.84) --
	(167.74,147.52) --
	(172.77,149.20) --
	(177.80,150.89) --
	(182.83,152.57) --
	(187.86,154.26) --
	(192.89,155.94) --
	(197.93,157.63) --
	(202.96,159.31) --
	(207.99,161.00) --
	(213.02,162.68) --
	(218.05,164.37) --
	(223.08,166.05) --
	(228.12,167.74) --
	(233.15,169.42) --
	(238.18,171.11) --
	(243.21,172.79) --
	(248.24,174.47) --
	(253.27,176.16) --
	(258.30,177.84) --
	(263.34,179.53) --
	(268.37,181.21) --
	(273.40,182.90) --
	(278.43,184.58) --
	(283.46,186.27) --
	(288.49,187.95) --
	(293.52,189.64) --
	(298.56,191.32) --
	(303.59,193.01) --
	(308.62,194.69) --
	(313.65,196.38) --
	(318.68,198.06) --
	(323.71,199.74) --
	(328.74,201.43) --
	(333.78,203.11) --
	(338.81,204.80) --
	(343.84,206.48) --
	(348.87,208.17) --
	(353.90,209.85) --
	(358.93,211.54) --
	(363.96,213.22) --
	(369.00,214.91) --
	(374.03,216.59) --
	(379.06,218.28) --
	(384.09,219.96) --
	(389.12,221.65) --
	(394.15,223.33) --
	(399.18,225.01) --
	(404.22,226.70);
\definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}

\path[fill=fillColor,fill opacity=0.30] ( 57.05,174.43) --
	( 62.08,174.80) --
	( 67.11,175.43) --
	( 72.14,175.95) --
	( 77.17,176.45) --
	( 82.20,177.01) --
	( 87.23,177.60) --
	( 92.27,178.07) --
	( 97.30,178.83) --
	(102.33,179.63) --
	(107.36,180.19) --
	(112.39,180.68) --
	(117.42,181.22) --
	(122.45,181.91) --
	(127.49,182.61) --
	(132.52,183.22) --
	(137.55,183.85) --
	(142.58,184.72) --
	(147.61,185.27) --
	(152.64,185.85) --
	(157.67,186.68) --
	(162.71,187.40) --
	(167.74,188.19) --
	(172.77,188.79) --
	(177.80,189.72) --
	(182.83,190.53) --
	(187.86,191.58) --
	(192.89,192.32) --
	(197.93,193.15) --
	(202.96,194.08) --
	(207.99,195.20) --
	(213.02,196.17) --
	(218.05,197.04) --
	(223.08,198.12) --
	(228.12,199.15) --
	(233.15,200.19) --
	(238.18,201.29) --
	(243.21,202.47) --
	(248.24,203.82) --
	(253.27,205.19) --
	(258.30,206.48) --
	(263.34,207.77) --
	(268.37,209.20) --
	(273.40,210.73) --
	(278.43,212.20) --
	(283.46,213.76) --
	(288.49,215.30) --
	(293.52,216.81) --
	(298.56,218.76) --
	(303.59,220.71) --
	(308.62,222.73) --
	(313.65,224.51) --
	(318.68,226.51) --
	(323.71,228.57) --
	(328.74,230.64) --
	(333.78,232.65) --
	(338.81,234.73) --
	(343.84,236.98) --
	(348.87,239.31) --
	(353.90,241.60) --
	(358.93,243.92) --
	(363.96,246.40) --
	(369.00,248.74) --
	(374.03,251.08) --
	(379.06,253.40) --
	(384.09,255.89) --
	(389.12,258.42) --
	(394.15,260.84) --
	(399.18,263.30) --
	(404.22,265.99) --
	(404.22,186.70) --
	(399.18,185.91) --
	(394.15,185.08) --
	(389.12,184.30) --
	(384.09,183.58) --
	(379.06,182.70) --
	(374.03,181.87) --
	(369.00,180.89) --
	(363.96,179.93) --
	(358.93,178.91) --
	(353.90,178.04) --
	(348.87,176.86) --
	(343.84,175.89) --
	(338.81,174.74) --
	(333.78,173.45) --
	(328.74,172.28) --
	(323.71,171.02) --
	(318.68,169.43) --
	(313.65,167.97) --
	(308.62,166.54) --
	(303.59,165.18) --
	(298.56,163.70) --
	(293.52,162.08) --
	(288.49,160.29) --
	(283.46,158.60) --
	(278.43,156.91) --
	(273.40,155.18) --
	(268.37,153.23) --
	(263.34,151.42) --
	(258.30,149.61) --
	(253.27,147.65) --
	(248.24,145.45) --
	(243.21,143.23) --
	(238.18,141.02) --
	(233.15,138.72) --
	(228.12,136.35) --
	(223.08,133.80) --
	(218.05,131.34) --
	(213.02,128.83) --
	(207.99,126.45) --
	(202.96,124.00) --
	(197.93,121.57) --
	(192.89,119.03) --
	(187.86,116.41) --
	(182.83,113.90) --
	(177.80,111.23) --
	(172.77,108.70) --
	(167.74,105.98) --
	(162.71,103.34) --
	(157.67,100.79) --
	(152.64, 98.10) --
	(147.61, 95.49) --
	(142.58, 92.64) --
	(137.55, 89.85) --
	(132.52, 87.02) --
	(127.49, 84.25) --
	(122.45, 81.44) --
	(117.42, 78.59) --
	(112.39, 75.96) --
	(107.36, 73.32) --
	(102.33, 70.44) --
	( 97.30, 67.62) --
	( 92.27, 64.83) --
	( 87.23, 61.80) --
	( 82.20, 58.96) --
	( 77.17, 56.21) --
	( 72.14, 53.52) --
	( 67.11, 50.65) --
	( 62.08, 47.79) --
	( 57.05, 45.08) --
	cycle;
\definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}

\path[fill=fillColor,fill opacity=0.50] ( 57.05,165.69) --
	( 62.08,166.26) --
	( 67.11,166.92) --
	( 72.14,167.65) --
	( 77.17,168.34) --
	( 82.20,169.03) --
	( 87.23,169.66) --
	( 92.27,170.38) --
	( 97.30,171.07) --
	(102.33,171.75) --
	(107.36,172.44) --
	(112.39,173.12) --
	(117.42,173.84) --
	(122.45,174.45) --
	(127.49,175.12) --
	(132.52,175.81) --
	(137.55,176.59) --
	(142.58,177.35) --
	(147.61,178.25) --
	(152.64,179.27) --
	(157.67,180.18) --
	(162.71,181.11) --
	(167.74,181.96) --
	(172.77,182.76) --
	(177.80,183.71) --
	(182.83,184.54) --
	(187.86,185.47) --
	(192.89,186.43) --
	(197.93,187.51) --
	(202.96,188.46) --
	(207.99,189.58) --
	(213.02,190.58) --
	(218.05,191.75) --
	(223.08,192.84) --
	(228.12,194.00) --
	(233.15,195.12) --
	(238.18,196.45) --
	(243.21,197.65) --
	(248.24,199.02) --
	(253.27,200.34) --
	(258.30,201.75) --
	(263.34,203.21) --
	(268.37,204.61) --
	(273.40,206.24) --
	(278.43,207.82) --
	(283.46,209.30) --
	(288.49,210.93) --
	(293.52,212.69) --
	(298.56,214.53) --
	(303.59,216.36) --
	(308.62,218.21) --
	(313.65,220.05) --
	(318.68,222.00) --
	(323.71,224.00) --
	(328.74,225.95) --
	(333.78,227.98) --
	(338.81,230.07) --
	(343.84,232.25) --
	(348.87,234.41) --
	(353.90,236.60) --
	(358.93,238.76) --
	(363.96,240.91) --
	(369.00,243.13) --
	(374.03,245.40) --
	(379.06,247.74) --
	(384.09,250.09) --
	(389.12,252.61) --
	(394.15,255.21) --
	(399.18,257.56) --
	(404.22,259.93) --
	(404.22,192.89) --
	(399.18,192.12) --
	(394.15,191.18) --
	(389.12,190.22) --
	(384.09,189.28) --
	(379.06,188.36) --
	(374.03,187.32) --
	(369.00,186.30) --
	(363.96,185.20) --
	(358.93,184.18) --
	(353.90,182.99) --
	(348.87,181.90) --
	(343.84,180.64) --
	(338.81,179.59) --
	(333.78,178.30) --
	(328.74,176.91) --
	(323.71,175.49) --
	(318.68,174.05) --
	(313.65,172.59) --
	(308.62,171.06) --
	(303.59,169.50) --
	(298.56,167.92) --
	(293.52,166.28) --
	(288.49,164.66) --
	(283.46,162.97) --
	(278.43,161.38) --
	(273.40,159.49) --
	(268.37,157.55) --
	(263.34,155.74) --
	(258.30,153.81) --
	(253.27,151.84) --
	(248.24,149.82) --
	(243.21,147.69) --
	(238.18,145.73) --
	(233.15,143.60) --
	(228.12,141.48) --
	(223.08,139.15) --
	(218.05,136.75) --
	(213.02,134.58) --
	(207.99,132.15) --
	(202.96,129.81) --
	(197.93,127.34) --
	(192.89,124.90) --
	(187.86,122.54) --
	(182.83,119.97) --
	(177.80,117.68) --
	(172.77,115.15) --
	(167.74,112.73) --
	(162.71,110.22) --
	(157.67,107.87) --
	(152.64,105.34) --
	(147.61,102.80) --
	(142.58,100.16) --
	(137.55, 97.55) --
	(132.52, 94.94) --
	(127.49, 92.32) --
	(122.45, 89.72) --
	(117.42, 87.08) --
	(112.39, 84.45) --
	(107.36, 81.80) --
	(102.33, 79.16) --
	( 97.30, 76.57) --
	( 92.27, 74.01) --
	( 87.23, 71.42) --
	( 82.20, 68.63) --
	( 77.17, 65.97) --
	( 72.14, 63.37) --
	( 67.11, 60.74) --
	( 62.08, 58.05) --
	( 57.05, 55.38) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.69, 34.03) --
	( 39.69,277.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57, 52.86) {3.7};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57, 96.58) {3.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,140.30) {3.9};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,184.02) {4.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,227.74) {4.1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,271.45) {4.2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.69, 34.03) --
	(421.57, 34.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 40.56, 20.31) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 90.87, 20.31) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (141.19, 20.31) {2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (191.50, 20.31) {3};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (241.82, 20.31) {4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (292.13, 20.31) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (342.45, 20.31) {6};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (392.76, 20.31) {7};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (230.63,  4.82) {Ln(Min. City Dist.)$_{t}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

>>>>

% Created by tikzDevice version 0.7.0 on 2014-09-25 14:22:36
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (433.62,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 52.48, 34.03) rectangle (421.57,277.03);
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[fill=fillColor] ( 52.48, 34.03) rectangle (421.57,277.03);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 69.26,108.08) --
	( 76.94,110.75) --
	( 81.21,112.23) --
	( 81.35,112.28) --
	( 94.75,116.93) --
	(103.21,119.87) --
	(108.87,121.84) --
	(112.14,122.97) --
	(118.51,125.19) --
	(123.77,127.01) --
	(127.53,128.32) --
	(130.04,129.19) --
	(138.05,131.97) --
	(158.20,138.97) --
	(171.57,143.61) --
	(171.70,143.66) --
	(174.96,144.79) --
	(175.86,145.11) --
	(185.97,148.62) --
	(188.46,149.48) --
	(195.56,151.95) --
	(205.05,155.24) --
	(205.06,155.25) --
	(209.59,156.82) --
	(209.87,156.92) --
	(211.41,157.45) --
	(212.10,157.69) --
	(212.80,157.94) --
	(212.89,157.97) --
	(213.53,158.19) --
	(213.69,158.24) --
	(215.24,158.78) --
	(220.60,160.64) --
	(222.23,161.21) --
	(222.43,161.28) --
	(224.02,161.83) --
	(228.32,163.33) --
	(228.78,163.49) --
	(233.22,165.03) --
	(235.00,165.65) --
	(235.50,165.82) --
	(236.76,166.26) --
	(238.27,166.78) --
	(238.97,167.03) --
	(239.94,167.36) --
	(240.65,167.61) --
	(240.90,167.70) --
	(240.95,167.71) --
	(241.36,167.86) --
	(244.68,169.01) --
	(246.54,169.65) --
	(247.54,170.00) --
	(248.75,170.42) --
	(249.31,170.62) --
	(250.77,171.12) --
	(251.67,171.44) --
	(252.68,171.79) --
	(253.66,172.13) --
	(254.85,172.54) --
	(254.86,172.54) --
	(255.67,172.83) --
	(256.23,173.02) --
	(256.77,173.21) --
	(257.49,173.46) --
	(257.71,173.54) --
	(258.26,173.73) --
	(258.74,173.89) --
	(259.12,174.02) --
	(259.38,174.11) --
	(259.99,174.33) --
	(260.56,174.52) --
	(260.79,174.60) --
	(262.27,175.12) --
	(262.38,175.16) --
	(263.62,175.59) --
	(263.78,175.64) --
	(265.81,176.35) --
	(267.16,176.82) --
	(267.27,176.85) --
	(267.90,177.08) --
	(269.02,177.46) --
	(269.24,177.54) --
	(269.50,177.63) --
	(270.00,177.80) --
	(271.24,178.23) --
	(271.44,178.30) --
	(271.47,178.31) --
	(271.89,178.46) --
	(272.97,178.83) --
	(273.00,178.84) --
	(273.30,178.95) --
	(274.10,179.23) --
	(274.51,179.37) --
	(275.15,179.59) --
	(275.85,179.83) --
	(276.45,180.04) --
	(276.57,180.09) --
	(277.67,180.47) --
	(277.74,180.49) --
	(278.30,180.69) --
	(278.99,180.93) --
	(279.37,181.06) --
	(280.17,181.34) --
	(281.01,181.63) --
	(281.75,181.88) --
	(282.04,181.99) --
	(282.56,182.17) --
	(282.59,182.17) --
	(282.73,182.22) --
	(283.17,182.38) --
	(283.67,182.55) --
	(284.33,182.78) --
	(284.38,182.80) --
	(284.78,182.94) --
	(285.47,183.18) --
	(285.59,183.22) --
	(285.79,183.29) --
	(285.93,183.34) --
	(285.96,183.35) --
	(286.40,183.50) --
	(286.76,183.63) --
	(286.94,183.69) --
	(287.11,183.75) --
	(287.40,183.85) --
	(287.56,183.90) --
	(287.64,183.93) --
	(288.93,184.38) --
	(289.17,184.46) --
	(289.98,184.74) --
	(290.06,184.77) --
	(290.15,184.80) --
	(290.68,184.98) --
	(290.90,185.06) --
	(291.07,185.12) --
	(291.16,185.15) --
	(291.99,185.44) --
	(292.53,185.63) --
	(292.56,185.64) --
	(293.19,185.86) --
	(293.72,186.04) --
	(294.42,186.28) --
	(294.46,186.30) --
	(295.07,186.51) --
	(295.58,186.69) --
	(296.54,187.02) --
	(296.64,187.06) --
	(296.96,187.17) --
	(297.07,187.21) --
	(297.55,187.37) --
	(297.61,187.39) --
	(297.93,187.50) --
	(298.07,187.55) --
	(298.13,187.57) --
	(298.19,187.59) --
	(298.21,187.60) --
	(298.32,187.64) --
	(298.88,187.83) --
	(299.55,188.07) --
	(300.83,188.51) --
	(301.02,188.58) --
	(301.08,188.60) --
	(301.48,188.74) --
	(301.54,188.76) --
	(301.64,188.79) --
	(301.73,188.83) --
	(302.00,188.92) --
	(302.17,188.98) --
	(302.49,189.09) --
	(302.51,189.10) --
	(302.54,189.11) --
	(302.55,189.11) --
	(302.59,189.12) --
	(302.62,189.13) --
	(302.72,189.17) --
	(302.80,189.20) --
	(302.80,189.20) --
	(303.19,189.33) --
	(303.42,189.41) --
	(303.79,189.54) --
	(304.00,189.61) --
	(304.46,189.77) --
	(305.92,190.28) --
	(306.03,190.32) --
	(306.63,190.53) --
	(307.38,190.79) --
	(307.50,190.83) --
	(307.76,190.92) --
	(308.06,191.02) --
	(308.22,191.08) --
	(308.71,191.25) --
	(309.07,191.37) --
	(309.23,191.43) --
	(309.24,191.43) --
	(309.36,191.48) --
	(309.39,191.49) --
	(309.44,191.50) --
	(310.04,191.71) --
	(310.57,191.90) --
	(310.65,191.92) --
	(310.74,191.95) --
	(310.97,192.03) --
	(311.29,192.15) --
	(311.41,192.19) --
	(312.93,192.71) --
	(312.98,192.73) --
	(313.47,192.90) --
	(313.56,192.93) --
	(314.18,193.15) --
	(314.39,193.22) --
	(314.46,193.25) --
	(314.61,193.30) --
	(314.93,193.41) --
	(315.17,193.49) --
	(315.66,193.66) --
	(315.81,193.72) --
	(315.92,193.75) --
	(316.04,193.79) --
	(316.27,193.88) --
	(316.28,193.88) --
	(316.31,193.89) --
	(316.40,193.92) --
	(316.53,193.97) --
	(316.54,193.97) --
	(316.73,194.03) --
	(316.73,194.03) --
	(317.05,194.15) --
	(317.72,194.38) --
	(317.91,194.44) --
	(318.05,194.49) --
	(318.31,194.58) --
	(318.59,194.68) --
	(318.98,194.82) --
	(319.05,194.84) --
	(319.19,194.89) --
	(319.36,194.95) --
	(319.71,195.07) --
	(319.91,195.14) --
	(319.93,195.15) --
	(320.06,195.19) --
	(320.17,195.23) --
	(320.20,195.24) --
	(320.30,195.27) --
	(320.38,195.30) --
	(320.46,195.33) --
	(320.79,195.44) --
	(320.87,195.47) --
	(321.03,195.53) --
	(321.25,195.60) --
	(321.56,195.71) --
	(321.69,195.76) --
	(321.81,195.80) --
	(321.97,195.85) --
	(322.34,195.98) --
	(322.35,195.99) --
	(322.38,196.00) --
	(322.44,196.02) --
	(322.47,196.03) --
	(322.55,196.06) --
	(322.98,196.21) --
	(323.15,196.26) --
	(323.39,196.35) --
	(323.51,196.39) --
	(323.64,196.43) --
	(323.74,196.47) --
	(324.03,196.57) --
	(324.31,196.67) --
	(324.91,196.88) --
	(326.25,197.34) --
	(326.31,197.36) --
	(326.44,197.41) --
	(326.69,197.49) --
	(326.98,197.59) --
	(327.12,197.64) --
	(327.38,197.73) --
	(327.45,197.76) --
	(327.62,197.82) --
	(328.36,198.07) --
	(328.71,198.20) --
	(328.89,198.26) --
	(329.00,198.30) --
	(329.34,198.41) --
	(330.21,198.72) --
	(330.77,198.91) --
	(330.92,198.96) --
	(331.77,199.26) --
	(332.05,199.35) --
	(332.77,199.61) --
	(333.03,199.70) --
	(333.16,199.74) --
	(333.59,199.89) --
	(335.17,200.44) --
	(335.96,200.71) --
	(336.21,200.80) --
	(336.98,201.07) --
	(337.10,201.11) --
	(337.64,201.30) --
	(339.32,201.88) --
	(339.85,202.06) --
	(340.50,202.29) --
	(340.63,202.33) --
	(341.25,202.55) --
	(341.62,202.68) --
	(341.97,202.80) --
	(342.00,202.81) --
	(342.05,202.83) --
	(342.45,202.97) --
	(342.53,202.99) --
	(343.04,203.17) --
	(343.17,203.22) --
	(343.85,203.45) --
	(343.87,203.46) --
	(343.95,203.49) --
	(344.16,203.56) --
	(344.46,203.67) --
	(344.63,203.72) --
	(344.93,203.83) --
	(345.02,203.86) --
	(345.07,203.88) --
	(345.10,203.89) --
	(345.51,204.03) --
	(345.57,204.05) --
	(346.09,204.23) --
	(346.39,204.34) --
	(347.80,204.83) --
	(348.20,204.96) --
	(348.41,205.04) --
	(348.87,205.20) --
	(348.92,205.21) --
	(349.60,205.45) --
	(351.33,206.05) --
	(351.43,206.09) --
	(351.56,206.13) --
	(351.74,206.20) --
	(351.87,206.24) --
	(353.20,206.70) --
	(353.44,206.78) --
	(353.54,206.82) --
	(354.59,207.18) --
	(357.17,208.08) --
	(357.38,208.15) --
	(357.90,208.33) --
	(357.93,208.34) --
	(358.21,208.44) --
	(358.75,208.63) --
	(359.57,208.92) --
	(359.62,208.93) --
	(360.33,209.18) --
	(360.36,209.19) --
	(360.85,209.36) --
	(361.40,209.55) --
	(362.06,209.78) --
	(362.35,209.88) --
	(362.48,209.93) --
	(362.58,209.96) --
	(363.30,210.21) --
	(363.33,210.22) --
	(363.40,210.24) --
	(364.54,210.64) --
	(365.21,210.87) --
	(366.77,211.42) --
	(366.99,211.49) --
	(368.17,211.90) --
	(368.73,212.10) --
	(372.78,213.50) --
	(373.25,213.67) --
	(374.25,214.01) --
	(374.25,214.01) --
	(374.55,214.12) --
	(374.76,214.19) --
	(375.05,214.29) --
	(375.30,214.38) --
	(375.66,214.50) --
	(375.91,214.59) --
	(376.54,214.81) --
	(376.88,214.93) --
	(377.80,215.25) --
	(378.36,215.44) --
	(378.50,215.49) --
	(378.91,215.63) --
	(379.95,215.99) --
	(381.22,216.44) --
	(381.23,216.44) --
	(381.92,216.68) --
	(381.95,216.69) --
	(382.82,216.99) --
	(383.24,217.14) --
	(383.51,217.23) --
	(384.09,217.43) --
	(384.17,217.46) --
	(384.29,217.50) --
	(384.73,217.65) --
	(386.66,218.32) --
	(386.77,218.36) --
	(390.32,219.59) --
	(394.80,221.15) --
	(396.85,221.86) --
	(404.07,224.37) --
	(404.80,224.62);
\definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}

\path[fill=fillColor,fill opacity=0.30] ( 69.26,174.00) --
	( 76.94,174.91) --
	( 81.21,175.28) --
	( 81.35,175.28) --
	( 94.75,176.82) --
	(103.21,177.55) --
	(108.87,178.21) --
	(112.14,178.55) --
	(118.51,179.36) --
	(123.77,179.97) --
	(127.53,180.45) --
	(130.04,180.72) --
	(138.05,181.83) --
	(158.20,184.48) --
	(171.57,186.12) --
	(171.70,186.12) --
	(174.96,186.43) --
	(175.86,186.59) --
	(185.97,188.24) --
	(188.46,188.71) --
	(195.56,189.94) --
	(205.05,191.47) --
	(205.06,191.47) --
	(209.59,192.51) --
	(209.87,192.54) --
	(211.41,192.84) --
	(212.10,193.02) --
	(212.80,193.13) --
	(212.89,193.15) --
	(213.53,193.30) --
	(213.69,193.33) --
	(215.24,193.64) --
	(220.60,194.57) --
	(222.23,194.95) --
	(222.43,194.98) --
	(224.02,195.30) --
	(228.32,196.22) --
	(228.78,196.37) --
	(233.22,197.33) --
	(235.00,197.73) --
	(235.50,197.81) --
	(236.76,198.12) --
	(238.27,198.42) --
	(238.97,198.51) --
	(239.94,198.70) --
	(240.65,198.90) --
	(240.90,198.95) --
	(240.95,198.96) --
	(241.36,199.05) --
	(244.68,199.85) --
	(246.54,200.21) --
	(247.54,200.41) --
	(248.75,200.77) --
	(249.31,200.94) --
	(250.77,201.35) --
	(251.67,201.62) --
	(252.68,201.84) --
	(253.66,202.15) --
	(254.85,202.44) --
	(254.86,202.44) --
	(255.67,202.67) --
	(256.23,202.80) --
	(256.77,202.98) --
	(257.49,203.17) --
	(257.71,203.20) --
	(258.26,203.36) --
	(258.74,203.50) --
	(259.12,203.66) --
	(259.38,203.76) --
	(259.99,203.84) --
	(260.56,203.97) --
	(260.79,204.00) --
	(262.27,204.53) --
	(262.38,204.57) --
	(263.62,204.89) --
	(263.78,204.92) --
	(265.81,205.57) --
	(267.16,205.98) --
	(267.27,206.00) --
	(267.90,206.19) --
	(269.02,206.47) --
	(269.24,206.53) --
	(269.50,206.63) --
	(270.00,206.83) --
	(271.24,207.27) --
	(271.44,207.33) --
	(271.47,207.33) --
	(271.89,207.39) --
	(272.97,207.77) --
	(273.00,207.78) --
	(273.30,207.93) --
	(274.10,208.20) --
	(274.51,208.30) --
	(275.15,208.47) --
	(275.85,208.69) --
	(276.45,208.85) --
	(276.57,208.88) --
	(277.67,209.23) --
	(277.74,209.26) --
	(278.30,209.41) --
	(278.99,209.61) --
	(279.37,209.72) --
	(280.17,209.90) --
	(281.01,210.17) --
	(281.75,210.39) --
	(282.04,210.51) --
	(282.56,210.73) --
	(282.59,210.74) --
	(282.73,210.80) --
	(283.17,210.98) --
	(283.67,211.13) --
	(284.33,211.34) --
	(284.38,211.36) --
	(284.78,211.50) --
	(285.47,211.75) --
	(285.59,211.80) --
	(285.79,211.87) --
	(285.93,211.89) --
	(285.96,211.90) --
	(286.40,212.01) --
	(286.76,212.10) --
	(286.94,212.15) --
	(287.11,212.19) --
	(287.40,212.28) --
	(287.56,212.36) --
	(287.64,212.40) --
	(288.93,212.86) --
	(289.17,212.95) --
	(289.98,213.19) --
	(290.06,213.22) --
	(290.15,213.26) --
	(290.68,213.45) --
	(290.90,213.53) --
	(291.07,213.59) --
	(291.16,213.62) --
	(291.99,213.93) --
	(292.53,214.13) --
	(292.56,214.14) --
	(293.19,214.38) --
	(293.72,214.62) --
	(294.42,214.91) --
	(294.46,214.93) --
	(295.07,215.21) --
	(295.58,215.42) --
	(296.54,215.77) --
	(296.64,215.82) --
	(296.96,215.91) --
	(297.07,215.95) --
	(297.55,216.15) --
	(297.61,216.18) --
	(297.93,216.29) --
	(298.07,216.34) --
	(298.13,216.36) --
	(298.19,216.38) --
	(298.21,216.39) --
	(298.32,216.43) --
	(298.88,216.63) --
	(299.55,216.84) --
	(300.83,217.35) --
	(301.02,217.42) --
	(301.08,217.44) --
	(301.48,217.63) --
	(301.54,217.65) --
	(301.64,217.68) --
	(301.73,217.71) --
	(302.00,217.78) --
	(302.17,217.84) --
	(302.49,217.96) --
	(302.51,217.97) --
	(302.54,217.98) --
	(302.55,217.98) --
	(302.59,218.00) --
	(302.62,218.02) --
	(302.72,218.07) --
	(302.80,218.10) --
	(302.80,218.10) --
	(303.19,218.24) --
	(303.42,218.32) --
	(303.79,218.45) --
	(304.00,218.54) --
	(304.46,218.72) --
	(305.92,219.26) --
	(306.03,219.30) --
	(306.63,219.55) --
	(307.38,219.82) --
	(307.50,219.86) --
	(307.76,219.99) --
	(308.06,220.05) --
	(308.22,220.15) --
	(308.71,220.34) --
	(309.07,220.51) --
	(309.23,220.58) --
	(309.24,220.58) --
	(309.36,220.63) --
	(309.39,220.64) --
	(309.44,220.65) --
	(310.04,220.93) --
	(310.57,221.18) --
	(310.65,221.20) --
	(310.74,221.23) --
	(310.97,221.37) --
	(311.29,221.50) --
	(311.41,221.54) --
	(312.93,222.17) --
	(312.98,222.19) --
	(313.47,222.35) --
	(313.56,222.39) --
	(314.18,222.61) --
	(314.39,222.66) --
	(314.46,222.67) --
	(314.61,222.71) --
	(314.93,222.88) --
	(315.17,222.95) --
	(315.66,223.09) --
	(315.81,223.13) --
	(315.92,223.16) --
	(316.04,223.21) --
	(316.27,223.29) --
	(316.28,223.29) --
	(316.31,223.29) --
	(316.40,223.32) --
	(316.53,223.37) --
	(316.54,223.38) --
	(316.73,223.47) --
	(316.73,223.47) --
	(317.05,223.60) --
	(317.72,223.94) --
	(317.91,224.00) --
	(318.05,224.03) --
	(318.31,224.13) --
	(318.59,224.22) --
	(318.98,224.34) --
	(319.05,224.36) --
	(319.19,224.40) --
	(319.36,224.48) --
	(319.71,224.64) --
	(319.91,224.74) --
	(319.93,224.75) --
	(320.06,224.83) --
	(320.17,224.87) --
	(320.20,224.88) --
	(320.30,224.92) --
	(320.38,224.96) --
	(320.46,224.99) --
	(320.79,225.13) --
	(320.87,225.16) --
	(321.03,225.25) --
	(321.25,225.37) --
	(321.56,225.45) --
	(321.69,225.50) --
	(321.81,225.57) --
	(321.97,225.64) --
	(322.34,225.80) --
	(322.35,225.81) --
	(322.38,225.82) --
	(322.44,225.86) --
	(322.47,225.88) --
	(322.55,225.93) --
	(322.98,226.04) --
	(323.15,226.10) --
	(323.39,226.21) --
	(323.51,226.27) --
	(323.64,226.34) --
	(323.74,226.38) --
	(324.03,226.53) --
	(324.31,226.67) --
	(324.91,226.96) --
	(326.25,227.49) --
	(326.31,227.51) --
	(326.44,227.55) --
	(326.69,227.67) --
	(326.98,227.78) --
	(327.12,227.86) --
	(327.38,228.02) --
	(327.45,228.05) --
	(327.62,228.10) --
	(328.36,228.30) --
